\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amssymb, amsthm, mathtools}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{tcolorbox}
\usepackage{enumitem}

\hypersetup{
  colorlinks=true,
  urlcolor=blue!60!black,
  linkcolor=blue!60!black,
  citecolor=blue!60!black
}

\titleformat{\section}{\large\bfseries\color{blue!50!black}}{\thesection.}{0.6em}{}
\titleformat{\subsection}{\bfseries\color{blue!50!black}}{\thesubsection.}{0.6em}{}

\newcommand{\Div}{\operatorname{div}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\W}{\mathcal{W}}
\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}
\newcommand{\eps}{\varepsilon}

\title{A Fixed-Point GAN Scheme for Weakly Non-Separable Mean Field Games}
\author{Hikmatullo Ismatov\\
\texttt{hikmatullo.ismatov@kaust.edu.sa}}
\date{\today}

\begin{document}
\maketitle

\section*{Purpose of this note}

This short note summarizes the current state of my project on extending GAN-based solvers for Mean Field Games (MFGs) to weakly non-separable Hamiltonians. I describe the main idea, the proposed algorithm, the contraction theorem, the numerical validation completed so far, and the main points that still need improvement before a formal submission.

The full draft, code, and slides are available at
\href{https://github.com/hikmatulloismatov1999/MFG-GAN-Paper}{\texttt{github.com/hikmatulloismatov1999/MFG-GAN-Paper}}.

\section{Main idea}

Deep learning solvers for Mean Field Games currently fall into two broad families. GAN-based solvers, such as APAC-Net and MFGAN, parameterize the density distributionally and provide Wasserstein-type convergence results, but they typically require the Hamiltonian to be separable, for example
\[
  H(x,\rho,p)=H_0(x,p)-f_0(x,\rho).
\]
On the other hand, physics-informed methods such as MFDGM can handle more general non-separable Hamiltonians by minimizing the PDE residual, but their convergence guarantees are weaker and usually do not provide explicit contraction rates.

The observation behind this project is simple. If the density variable inside the non-separable part is frozen, then the resulting subproblem becomes separable in the sense required by the inner GAN solver. This motivates an outer fixed-point iteration for Hamiltonians of the form
\[
  H(x,\rho,p)=H_0(x,p)-f_0(x,\rho)+\eps R(x,\rho,p),
\]
where $\eps>0$ measures the strength of the non-separable perturbation.

\section{Proposed algorithm}

The method is a damped Picard-type iteration on the density. At each outer step, the density is frozen inside the residual term, and the resulting separable MFG is solved using an inner GAN-based solver.

\begin{tcolorbox}[colback=blue!4, colframe=blue!50!black, arc=2pt]
\textbf{Extended-MFGAN fixed-point scheme.}

\medskip
\textbf{Input.} A Hamiltonian of the form
\[
  H(x,\rho,p)=H_0(x,p)-f_0(x,\rho)+\eps R(x,\rho,p),
\]
diffusion coefficient \(\nu\geq 0\), terminal cost \(g\), initial density \(\rho_0\), an inner GAN solver, and the number of outer iterations \(K\).

\medskip
\textbf{Initialization.} Set \(\rho^0\leftarrow \rho_0\).

\medskip
\textbf{Iteration.} For \(k=0,1,\dots,K-1\), do the following:
\begin{enumerate}[noitemsep]
  \item Define the frozen effective Hamiltonian
  \[
    H^k(x,p):=H_0(x,p)+\eps R(x,\rho^k(x,t),p).
  \]
  Once \(\rho^k\) is fixed, this Hamiltonian depends only on \((x,p)\).

  \item Solve the corresponding separable MFG using the inner GAN solver:
  \[
    (\varphi^{k+1},\rho^{k+1})
    \leftarrow \mathrm{APAC\text{-}Net}(H^k,f_0,g,\rho_0).
  \]
\end{enumerate}

\medskip
\textbf{Output.} Return \((\varphi^K,\rho^K)\).
\end{tcolorbox}

When $\eps=0$, the effective Hamiltonian is independent of the previous density, and the scheme reduces to the original separable GAN solver after one outer step. For $\eps>0$, the additional cost is $K$ inner solves. Once a contraction factor $\kappa_\eps<1$ is known, the number of outer iterations needed to reach accuracy $\delta$ is of order
\[
  K \sim \frac{\log(1/\delta)}{\log(1/\kappa_\eps)}.
\]

\subsection*{Remark: the role of \texorpdfstring{$\eps$}{eps}}

It is important to be clear about the role of the parameter $\eps$ and of the word \emph{weakly} in the title.

The freeze-$\rho$ step of the algorithm is well defined for \emph{any} non-separable Hamiltonian: once $\rho^k$ is fixed inside the residual, $H^k(x,p)$ is automatically a function of $(x,p)$ only, and any separable inner solver can be applied. There is no structural obstruction to running the scheme on a fully non-separable problem.

The role of $\eps$ is therefore not algorithmic; it is about \emph{convergence of the outer fixed-point map}. The smallness condition $\eps L_R<\lambda$ (in the density-only case, with the obvious analogue in general) is what ensures that the map
\[
  \mathcal{T}: \bar\rho \;\longmapsto\;
  \rho \;=\; \text{density component of the separable MFG with frozen}\ \bar\rho
\]
is a contraction in $L^2$. Without such a smallness condition, $\mathcal{T}$ may fail to be contractive: the outer iteration is still well defined, but it can oscillate or grow geometrically rather than converge. This is shown explicitly in the bilinear example of Section~4, where the linearized outer map has operator norm $\eps|1-\eps|/\lambda$, exceeding one as soon as $\eps L_R\geq\lambda$.

In short, the word \emph{weakly} refers to a convergence condition on the outer map. It is not a structural restriction on the underlying MFG and does not exclude any particular Hamiltonian a priori; it simply identifies the regime in which the outer fixed-point iteration is guaranteed to converge with the explicit rate stated below.

\section{Convergence result}

\subsection{Assumptions}

The current theorem is proved under the following assumptions.

\begin{enumerate}[leftmargin=*]
  \item $H_0$ is $c_0$-strongly convex in $p$.
  \item $f_0$ satisfies the Lasry--Lions monotonicity condition with constant $\lambda>0$.
  \item The perturbation $R$ is Lipschitz on the admissible region, with constants $L_R$ in the density variable and $L_{R,p}$ in the momentum variable.
  \item $\nabla_p R$ is $L_{p\rho}$-Lipschitz with respect to the frozen density.
  \item The densities satisfy uniform bounds
  \[
    0<\rho_{\min}\leq \rho \leq \rho_{\max},
  \]
  and the value functions satisfy a bounded-momentum estimate
  \[
    \norm{\nabla\varphi}_{L^\infty}\leq u_{\max}.
  \]
\end{enumerate}

The bounded-momentum assumption is natural for coercive Hamilton--Jacobi equations, but I still need to justify it more carefully in the manuscript, either by citing standard viscosity theory or by deriving the estimate in the specific setting considered here.

\subsection{GAN-tractable regime}

The Hamiltonian is said to be in the GAN-tractable regime if
\[
  \alpha_\eps := c_0\rho_{\min}-3\eps L_{R,p}\rho_{\max}>0,
\]
and
\[
  \kappa_\eps
  :=
  \frac{
  \eps L_R+
  \sqrt{\eps^2L_R^2+
  \lambda\eps^2L_{p\rho}^2\rho_{\max}^2/\alpha_\eps}
  }{2\lambda}
  <1.
\]

In the density-only case $R=R(x,\rho)$, the momentum-dependent constants vanish, and the condition reduces to the simpler threshold
\[
  \kappa=\frac{\eps L_R}{\lambda}<1,
\]
which is the threshold used in the numerical experiments of Section~5.

\subsection{Main contraction theorem}

Under the assumptions above and the GAN-tractable condition, the outer fixed-point map is an $L^2$ contraction:
\[
  \norm{\rho^{k+1}-\rho^*}_{L^2((0,T)\times\Omega)}
  \leq
  \kappa_\eps
  \norm{\rho^k-\rho^*}_{L^2((0,T)\times\Omega)}.
\]
Here $\rho^*$ denotes the fixed point, equivalently the density component of the solution to the original weakly non-separable MFG.

Since $\Omega$ is bounded, this also gives a Wasserstein-type estimate of the form
\[
  \W_2(\rho^k(t,\cdot),\rho^*(t,\cdot))
  \leq C\kappa_\eps^{k/2},
\]
with a constant depending on the domain and the density bounds.

I currently state this as an explicit convergence rate for a GAN-based solver in the weakly non-separable setting. Before making this claim strongly in a submission, I will compare it carefully with the existing policy-iteration and non-separable MFG literature, in particular Lavigne--Pfeiffer (2023).

\subsection{Proof strategy}

The proof uses the Lasry--Lions duality identity for two MFG solutions $(\varphi_i,\rho_i)$ corresponding to two frozen densities $\bar\rho_i$. After subtracting the two systems and computing
\[
  \frac{d}{dt}\int_\Omega (\varphi_1-\varphi_2)(\rho_1-\rho_2)\,dx,
\]
the diffusion terms cancel, and integration by parts gives a residual identity of the form
\[
  \int_0^T(A+C)\,dt+
  \int_0^T B\,dt=0.
\]
The monotonicity of $f_0$ gives
\[
  B\leq -\lambda\norm{\rho_1-\rho_2}_{L^2}^2.
\]
The strongly convex part of the Hamiltonian gives a favorable sign, while the perturbative terms involving $R$ are controlled by
\[
  \eps L_R,\qquad \eps L_{R,p},\qquad \eps L_{p\rho}.
\]
Combining these estimates leads to an inequality of the form
\[
  \lambda\norm{\delta\rho}_{L^2}^2
  \leq
  \eps L_R
  \norm{\delta\bar\rho}_{L^2}
  \norm{\delta\rho}_{L^2}
  +
  B_\eps
  \norm{\delta\bar\rho}_{L^2}^2.
\]
A quadratic-formula argument then yields the contraction factor $\kappa_\eps$, and the Banach fixed-point theorem gives convergence of the outer iteration.

\section{Sharpness in a model example}

For the bilinear family
\[
  H_\eps(\rho,p)=\frac12p^2-p+\eps\rho p,
\]
linearization around the no-drift uniform equilibrium
\[
  (\rho^*,p^*)=(1,1-\eps)
\]
leads to an explicit Fourier-mode calculation. In this example, the linearized outer map has operator norm
\[
  \frac{\eps|1-\eps|}{\lambda},
\]
which matches the predicted contraction rate in the corresponding regime. In particular, when $\eps L_R > \lambda$ the operator norm exceeds one, so the linearized iteration grows geometrically rather than decaying. This shows that the threshold $\eps L_R < \lambda$ is necessary in the linearized regime, not merely a technical convenience.

\section{Numerical validation completed so far}

At this stage, the numerical experiments validate the analytically derived linearized outer map. They do not yet implement the full APAC-Net or MFGAN inner solver.

The current experiments are:

\begin{enumerate}[leftmargin=*]
  \item \textbf{Separable limit, $\eps=0$.} The error drops to machine precision in one outer step, confirming that the method reduces to the separable GAN solver in this limit.

  \item \textbf{Bilinear MFG-LWR model.} For $\lambda=0.2$, the empirical contraction factor agrees with the predicted value
  \[
    \kappa=\frac{\eps|1-\eps|}{\lambda}
  \]
  across the tested range of $\eps$.

  \item \textbf{Density-only perturbation.} The empirical transition occurs at the predicted threshold
  \[
    \eps L_R=\lambda,
  \]
  and the observed contraction matches the theoretical rate.
\end{enumerate}

These experiments support the sharpness of the contraction theorem in the linearized setting. However, they should be presented as validation of the outer fixed-point theory, not as a complete neural-network implementation.

\section{Main limitations}

I do not yet consider the manuscript fully ready for journal submission. The main issues are the following.

\begin{enumerate}[leftmargin=*]
  \item \textbf{No full neural-network pipeline yet.} The current experiments use the analytically derived linearized map. They do not train an APAC-Net or MFGAN inner solver end-to-end. A finite-difference reference experiment would already strengthen the paper, and a full GAN implementation would be ideal.

  \item \textbf{The factor $3$ in the GAN-tractable condition.} The factor appears from a three-way decomposition in the proof. I kept it to make the absorption argument transparent, but it may be possible to improve it using a sharper Young inequality argument.

  \item \textbf{Bounded-momentum assumption.} This is needed when $R$ depends on $p$, for example in the bilinear case $R=\rho p$. I need to justify this assumption more carefully.

  \item \textbf{Novelty of the explicit-rate claim.} I will check this claim against Lavigne--Pfeiffer (2023) and the broader policy-iteration literature before making any novelty statement in the abstract or introduction.

  \item \textbf{Title and positioning.} Since the full GAN pipeline is not yet implemented, a conservative title such as
  \begin{center}
  \emph{A Fixed-Point GAN Scheme for Weakly Non-Separable Mean Field Games}
  \end{center}
  may be more accurate than a title that suggests a complete implemented GAN method.
\end{enumerate}

\section{Questions for discussion}

I would especially appreciate your advice on the following points.

\begin{enumerate}[leftmargin=*]
  \item Does the bilinear-case argument, in particular the Fourier-mode calculation for
  $H_\eps=\frac12p^2-p+\eps\rho p$, look mathematically correct?

  \item Is the bounded-momentum assumption acceptable in this setting, or should I derive it explicitly from standard estimates for coercive Hamilton--Jacobi equations?

  \item Do you think a finite-difference reference experiment is enough before submission, or should I first implement the full neural-network inner solver?

  \item Once the mathematical and experimental parts are strengthened, what would be the most appropriate publication strategy for this project?

  \item Would you recommend changing the title or positioning of the paper to make the current contribution more precise and honest?
\end{enumerate}

\section{Proposed next steps}

If you think the direction is promising, my proposed next steps are:

\begin{enumerate}[leftmargin=*]
  \item revise the proof according to your comments;
  \item add a finite-difference reference experiment for the bilinear model;
  \item make the novelty claim more precise after checking the closest related work;
  \item prepare a cleaner manuscript version for further feedback;
  \item discuss the publication strategy once the mathematical proof and experiments are in stronger shape.
\end{enumerate}

I would value the chance to discuss any of these points in person at your convenience.

\end{document}
