\section{Introduction}
\label{sec:intro}

Mean Field Games (MFGs) \citep{lasry2007mean, huang2006large} have emerged as
a fundamental tool for modeling the collective behavior of large populations
of rational agents, from autonomous vehicles navigating congested roads
\citep{huang2019mfg} to investors competing in financial markets
\citep{carmona2018probabilistic} and agents in industrial and engineering systems.
At equilibrium, each agent plays optimally against the aggregate effect of the
population, yielding a Nash equilibrium described by a coupled system of
a backward Hamilton-Jacobi-Bellman (HJB) equation and a forward Fokker-Planck
(FP) equation:
\begin{align}
  -\partial_t \varphi - \nu\Delta\varphi + H(x,\rho,\nabla\varphi) &= 0,
  \quad \text{in } (0,T)\times\Omega, \label{eq:HJB}\\
  \partial_t \rho - \nu\Delta\rho - \Div\!\bigl(\rho\,\nabla_p H(x,\rho,\nabla\varphi)\bigr)
  &= 0, \quad \text{in } (0,T)\times\Omega, \label{eq:FP}
\end{align}
where $\varphi$ is the agents' value function, $\rho$ is the population density,
and $H$ is the Hamiltonian encoding the game's interaction structure.
Solving this system in high dimensions is a central computational challenge
in the field.

\paragraph{The power and limits of GAN-based solvers.}
A major advance came with the observation that, when the Hamiltonian is
\emph{separable}, i.e., $H(x,\rho,p) = H_0(x,p) - f_0(x,\rho)$,
the MFG system can be reformulated as a min-max saddle-point problem
\citep{cao2021connecting}.
This connects MFGs structurally to Wasserstein GANs, enabling
algorithms such as APAC-Net \citep{lin2021apac} and MFGANs
\citep{ruthotto2020machine} that learn the equilibrium density
\emph{distributionally} (via a generator network) and provide
Wasserstein-type convergence guarantees.

However, the separability assumption is not merely a technical convenience:
it is a hard structural requirement.
The Hopf formula, which underlies the GAN reformulation, breaks down the moment
$H$ couples $\rho$ and $p$ jointly.
Many of the most important MFG models in practice are \emph{non-separable}.
The canonical example is the MFG-LWR traffic flow model \citep{huang2019mfg},
where congestion enters the dynamics through the term $(1-\rho)p$,
yielding a Hamiltonian
\[
  H(x,\rho,p) = \tfrac{1}{2}\norm{p}^2 - (1-\rho)\,p
\]
that couples density and momentum inseparably.
The usual separable GAN formulation cannot be applied directly to such
problems.

\paragraph{The cost of going beyond separability.}
The recent MFDGM method \citep{assouline2023deep} addresses non-separable
Hamiltonians by directly minimizing PDE residuals via physics-informed
neural networks, removing any structural requirement on $H$.
This is a genuine advance, but it comes at a price:
MFDGM approximates $\rho$ \emph{pointwise} rather than distributionally,
and its existing convergence theory is stated in $L^p$ ($p<2$) without an
explicit geometric rate.
Current methods therefore face a practical dichotomy:
adversarial methods have distributional structure but require separability,
whereas residual-minimization methods are more flexible but come with
different guarantees.

\paragraph{This paper: a fixed-point reduction.}
We show that this dichotomy is not fundamental.
It is a consequence of treating the non-separable Hamiltonian as monolithic.
Our key insight is elementary: \emph{if the population density $\rho$ is
temporarily frozen, any non-separable Hamiltonian becomes separable.}
This observation turns the non-separable MFG into a sequence of separable
subproblems, each compatible with existing adversarial MFG solvers, with the
density updated between iterations.

To make this precise, we introduce the class of
\emph{weakly non-separable Hamiltonians}, where the coupling between $\rho$
and $p$ is parameterized by a strength $\eps \geq 0$.
We prove that, when this coupling is controlled by the Lasry--Lions
monotonicity of the game and by the strong convexity of the base Hamiltonian,
the exact outer fixed-point map is a contraction in $L^2$.  The resulting
condition is explicit.  In the density-only subcase, it reduces to the clean
rate $\varepsilon L_R/\lambda$, and this threshold is sharp.  The result should
be read as an outer-map reduction theorem: it identifies when a weakly
non-separable MFG can be reduced to separable, GAN-compatible subproblems.  It
does not by itself prove convergence of stochastic adversarial training.

\paragraph{Contributions.}
\begin{enumerate}
  \item \textbf{Weakly non-separable Hamiltonians.}
    We introduce a formal interpolation between separable and non-separable
    MFGs via a coupling parameter $\eps$, and identify the GAN-tractable
    regime as an explicit weak-coupling criterion for the outer fixed-point
    reduction.  In the density-only subcase this criterion reduces to
    $\eps L_R < \lambda$.

  \item \textbf{Fixed-point wrapper.}
    We formulate a fixed-point outer iteration that decomposes the
    non-separable MFG into a sequence of separable subproblems, each compatible
    with existing adversarial MFG solvers (e.g., APAC-Net).  When $\eps=0$,
    the outer wrapper reduces to a single separable inner solve.

  \item \textbf{Outer contraction theorem.}
    We prove via a Lasry--Lions duality argument that the exact outer
    fixed-point iteration is an $L^2$ contraction under an explicit
    weak-coupling condition.  For density-only residuals, the contraction rate
    reduces to $\kappa=\eps L_R/\lambda<1$, and Wasserstein convergence follows
    from standard $L^2$-to-transport estimates.

  \item \textbf{Sharpness in the density-only subcase.}
    We prove that the clean threshold $\eps L_R < \lambda$ is necessary and
    sharp for a linearized ergodic density-only family on the torus.

  \item \textbf{Numerical validation.}
    Across three deterministic linearized experiments (separable limit,
    bilinear MFG-LWR, density-only sweep), the empirical outer-map contraction
    rate matches the predicted linearized rate, including the two-threshold
    behavior of the bilinear MFG-LWR family.
\end{enumerate}

\paragraph{Paper organization.}
\Cref{sec:prelim} reviews MFGs, GAN-based solvers, and MFDGM, and
formalizes the gap between them.
\Cref{sec:related} positions our contribution within the deep-learning MFG
literature.
\Cref{sec:weak} introduces weakly non-separable Hamiltonians and the
GAN-tractable regime.
\Cref{sec:algorithm} presents the fixed-point outer algorithm.
\Cref{sec:convergence} develops the convergence theory.
\Cref{sec:experiments} presents numerical results.
\Cref{sec:conclusion} concludes with directions for future work.
