\section{The Fixed-Point Outer Algorithm}
\label{sec:algorithm}

\subsection{Key Idea: Freezing the Density}

The fundamental obstacle to applying GAN methods to non-separable MFGs is
the joint dependence of $H$ on $(\rho, p)$, which prevents the saddle-point
formulation \eqref{eq:saddle} from being derived.
Our observation is that this obstacle disappears as soon as $\rho$ is held fixed.

If $\rho$ is treated as a known function from the previous iteration,
the effective Hamiltonian (using the decomposition of \Cref{def:weak_nonsep})
\begin{equation}\label{eq:Hk}
  H^k(x,p) \coloneqq H_0(x,p) + \eps\, R(x,\rho^k(x,t),p)
\end{equation}
depends only on $(x,p)$ and is therefore separable in the sense required
for GAN-based methods. The non-separable MFG thus reduces to a sequence
of separable subproblems, one per outer iteration.

\subsection{Effective Saddle-Point at Step $k$}

Given frozen density $\rho^k$, the MFG subproblem at iteration $k$ is:
\begin{equation}\label{eq:saddle_k}
  \inf_{\rho}\, \sup_{\varphi}\;
  \Bigl\{
    \E\bigl[\partial_t\varphi + \nu\Delta\varphi - H^k(x,\nabla\varphi)\bigr]
    + \E[\varphi(0,\cdot)] - \E_{x\sim\rho_T}[\varphi(T,x)]
    + \E[f_0(\cdot,\rho)]
  \Bigr\},
\end{equation}
where $H^k$ is defined in \eqref{eq:Hk}. This is the same separable
saddle-point structure as \eqref{eq:saddle}, with $H_0$ replaced by
$H^k$. Thus, at the level of the mathematical subproblem, any solver
designed for separable adversarial MFG formulations can be used as the
inner subroutine.

\subsection{Algorithm}

\begin{algorithm}[H]
\caption{Fixed-point reduction with a GAN-compatible inner solver}
\label{alg:main}
\begin{algorithmic}[1]
\Require Hamiltonian $H = H_0 - f_0 + \eps R$, diffusion $\nu \geq 0$,
         terminal cost $g$, initial density $\rho_0$
\Require separable inner solver (e.g., APAC-Net), outer iterations $K$,
         inner iterations $N$
\State Initialize: $\rho^0 \leftarrow \rho_0$
\For{$k = 0, 1, \ldots, K-1$}
  \State Compute effective Hamiltonian:
    $H^k(x,p) = H_0(x,p) + \eps\, R(x, \rho^k(x,\cdot), p)$
  \State Run the inner solver for $N$ iterations on the separable MFG
    with Hamiltonian $H^k$ and interaction $f_0$:
    \[
      (\rho^{k+1}, \varphi^{k+1}) \leftarrow \textsc{APAC-Net}(H^k, f_0, g, \rho_0, N)
    \]
\EndFor
\State \Return $(\rho^K, \varphi^K)$
\end{algorithmic}
\end{algorithm}

\subsection{Special Cases and Connections}

\paragraph{Separable limit.}
When $\eps = 0$, we have $H^k = H_0$ for all $k$, so the outer map is
constant and the wrapper reduces to one separable inner solve.

\paragraph{Bilinear coupling.}
When $R(x,\rho,p) = \rho\cdot p$ (as in the MFG-LWR model), the frozen
Hamiltonian is $H^k(x,p) = H_0(x,p) + \eps\,\rho^k(x,t)\,p$.
Since $R$ is linear in $\rho$, each outer update is the exact solution to
the subproblem given $\rho^k$, and the iteration is a Picard scheme
on the bilinear coupling.

\paragraph{Connection to policy iteration.}
The policy iteration algorithm of \citet{lavigne2023policy} for non-separable
MFGs also iterates over a sequence of decoupled linear PDEs.
The present reduction can be viewed as the distributional analogue when
the frozen subproblems are solved by a generator-based adversarial method.
In that case it replaces finite-difference PDE solves with neural inner
solves while keeping the same outer Picard structure.

\subsection{Computational Cost}

The total cost is $K$ times the cost of one frozen separable inner solve.
By \Cref{thm:main}, the exact outer iteration converges geometrically with
factor $\kappa_\eps$. To reach tolerance $\delta$, at most
\[
  K = \left\lceil \frac{\log(1/\delta)}{\log(1/\kappa_\eps)} \right\rceil
\]
outer iterations are needed, up to the initial error constant. In the
GAN-tractable regime $\kappa_\eps < 1$, this is a controlled multiplicative
overhead over a single separable solve. In the density-only subcase,
$\kappa_\eps$ reduces to the simpler expression $\eps L_R/\lambda$.
