\section{Numerical Experiments}
\label{sec:experiments}

We evaluate Extended-MFGAN on three experiments designed to:
(1) validate the convergence theorem,
(2) demonstrate superiority over MFDGM in the GAN-tractable regime,
(3) characterize the phase transition at $\eps L_R = \lambda$.

\subsection{Setup}

All experiments use the following architecture for the inner GAN:
a generator $G_\theta$ with 3 hidden layers of 128 neurons (ReLU),
and a critic $D_\omega$ with 3 hidden layers of 128 neurons (Softplus),
both trained with Adam at learning rate $10^{-4}$.
Outer iterations: $K = 20$; inner iterations: $N = 5000$ per outer step.

\subsection{Experiment 1: Separable Limit ($\eps = 0$, Analytic Solution)}

We first verify that Extended-MFGAN recovers APAC-Net exactly when $\eps = 0$,
using the analytic MFG solution from \citet{lin2021apac}:
\[
  \varphi(t,x) = \norm{x}^2/2 - d\cdot t, \quad
  \rho(t,x) = (2\pi)^{-d/2} e^{-\norm{x}^2/2},
\]
in $\Omega = [-2,2]^d$, $T = 1$, $\nu = 1$.

\paragraph{Metric.} We report the relative $L^2$ error and
$\mathcal{W}_2$ distance to the exact solution on a $100\times 100$ grid.

\paragraph{Expected result.}
Single outer iteration achieves the same accuracy as APAC-Net
(\Cref{cor:apacnet}). \todo{Fill in table with actual numbers.}

\subsection{Experiment 2: Traffic Flow Benchmark (MFG-LWR)}

We apply Extended-MFGAN to the MFG-LWR system \eqref{eq:decomp}
with non-separable Hamiltonian $H = \tfrac{1}{2}\norm{p}^2 - (1-\rho)p$
($\eps = 1$, bilinear coupling). Spatial domain $\Omega = [0,1]$,
$T = 1$, terminal cost $g = 0$, initial density
$\rho_0(x) = 0.2 - 0.6\exp(-\tfrac{1}{2}(\tfrac{x-0.5}{0.1})^2)$.

We run both deterministic ($\nu = 0$) and stochastic ($\nu = 0.5$) cases.

\paragraph{Comparison.}
We compare against:
\begin{itemize}
  \item MFDGM \citep{assouline2023deep} (Algorithm~1 in that paper),
  \item APAC-Net \citep{lin2021apac} applied directly (expected to fail — baseline),
  \item Extended-MFGAN (ours).
\end{itemize}
Metrics: HJB/FP residual loss, fundamental diagram validation (flux $q = \rho u$),
and $\mathcal{W}_2$ distance between iterations.

\paragraph{Expected result.}
Extended-MFGAN converges faster than MFDGM in $\mathcal{W}_2$ (outer contraction
$\kappa < 1$), while APAC-Net fails to converge (non-separable $H$).
\todo{Fill in figures: convergence curves, density/cost snapshots, fundamental diagram.}

\subsection{Experiment 3: Phase Transition at $\eps L_R = \lambda$}

We vary $\eps \in \{0, 0.2, 0.4, 0.6, 0.8, 1.0, 1.2\}$ and for each value:
\begin{enumerate}
  \item Measure the outer contraction factor $\kappa_{\text{emp}}$ empirically
    (ratio of successive $\mathcal{W}_2$ errors),
  \item Compare to the theoretical bound $\kappa = \eps L_R / \lambda$.
\end{enumerate}
We expect a clear phase transition: for $\eps L_R < \lambda$, convergence is
geometric; for $\eps L_R \geq \lambda$, the outer iteration diverges and
MFDGM should be preferred.

\paragraph{Expected result.}
A plot of $\kappa_{\text{emp}}$ vs $\eps$ showing the transition at
the predicted threshold $\eps^* = \lambda / L_R$.
\todo{Fill in phase transition plot.}

\subsection{Experiment 4: High-Dimensional Scaling}

We test Extended-MFGAN on the analytic MFG in dimensions $d = 2, 50, 100, 200$
with weak coupling ($\eps = 0.5$, $R(x,\rho,p) = \rho\cdot\norm{p}^2/2$).
We compare relative error and wall-clock time against MFDGM.

\paragraph{Expected result.}
Extended-MFGAN achieves comparable or better accuracy at lower
computational cost (fewer total neural network evaluations due to GAN efficiency).
\todo{Fill in scaling table.}
