Existing deep learning solvers for Mean Field Games fall into two families.
GAN-based methods learn population densities distributionally and come with
Wasserstein convergence guarantees, but are restricted to Hamiltonians with
separable structure. Physics-informed methods handle non-separable Hamiltonians
but provide only weak pointwise approximations with no explicit convergence rate.
We introduce the class of \emph{weakly non-separable Hamiltonians}, where the
coupling between density and momentum is measured by a single parameter,
and propose Extended-MFGAN, a fixed-point GAN iteration that handles this class
without abandoning the distributional learning of GAN-based solvers.
Our main result is an $L^2$ contraction theorem with explicit geometric rate
determined by the ratio of coupling strength to Lasry-Lions monotonicity,
which yields Wasserstein-2 convergence with the same exponential rate up to
the standard $L^2$-to-$\mathcal{W}_2$ square-root scaling.
This is, to our knowledge, the first explicit convergence rate for a
deep learning MFG solver in the non-separable setting.
We further prove the rate is sharp on a parameterised bilinear traffic-flow
family, give a linearised counterexample showing the GAN-tractable condition
is necessary, and validate the rate numerically across three Mean Field
Games, recovering the predicted phase transitions to four-digit accuracy
in the linearised regime.

\smallskip
\noindent\textit{Keywords:} Mean Field Games, Generative Adversarial Networks,
Non-Separable Hamiltonians, Wasserstein Convergence, Lasry-Lions Theory,
Traffic Flow.
